How cryptic is cryptic diversity? Machine learning approaches to classifying morphological variation in \textit{Emys marmorata} (Testudinoidea, Emydidae).

### 2014-12-02 doc/draft_turtle.tex
importance and selection plots

For both the LDA and multinomial logistic regression models, increasing model complexity increased cumulative percent variation necessary to best model the differing classification schemes FIGURE OF CUMMULATIVE. The high variance in optimal number of PCs used as predictors between schemes may represent either ease of fitting that particular model or that the data was too noising to accurately fit any model beyond the simplest.

As part of fitting a random forest model, a ranking of variable importance is also determined. Interestingly, the the order of variable importance is not the same as the order of principal components. This means that the principal components that best describe the differences between the various classes are not aligned with the principal components which describe the largest amount of variance. This result would be the case if variation between classes was extremely fine grained and not a part of the principal function or form of the plastron, which makes sense given that the plastron is involved in both protection and aquadynamics and not mate choice \citep{Germano2009,Holland1992,Lubcke2007,Rivera2008}.

@@

% tabel of RFS choice for random forest

@@

>>>>

For both the LDA and multinomial logistic regression models, increasing model complexity increased cumulative percent variation necessary to best model the differing classification schemes (Fig. \ref{fig:sel}). The high variance in optimal number of PCs used as predictors between schemes may represent either ease of fitting that particular model or that the data was too noising to accurately fit any model beyond the simplest.

As part of fitting a random forest model, a ranking of variable importance is also determined. Interestingly, the the order of variable importance is not the same as the order of principal components (Fig. \ref{fig:var_imp}). This means that the principal components that best describe the differences between the various classes are not aligned with the principal components which describe the largest amount of variance. This result would be the case if variation between classes was extremely fine grained and not a part of the principal function or form of the plastron, which makes sense given that the plastron is involved in both protection and aquadynamics and not mate choice \citep{Germano2009,Holland1992,Lubcke2007,Rivera2008}.

@@

@@

\begin{figure}[ht]
  \centering
  \includegraphics[height = \textheight, width = \textwidth, keepaspectratio = true]{figure/sel_val}
  \caption{CAPTION}
  \label{fig:sel}
\end{figure}

\begin{figure}[ht]
  \centering
  \includegraphics[height = \textheight, width = \textwidth, keepaspectratio = true]{figure/var_imp}
  \caption{Variable importance from the random forest models for each of the six classification schemes. Importance is measured as the mean decrease in Gini Index, which is a measure of the strength by which that variable determines CART structure. Indices that are farther to the right indicate greater variable importance.}
  \label{fig:var_imp}
\end{figure}
